Supplementary Materials

### 2020-06-24 analysis/analysis.Rmd
Added para-orientation model

@@

It's clearly skewed, and negative display duration are impossible, so will fit a `glm` with `family = 'lognormal'`.

```{r cache=TRUE, fig.cap = "Data are the root-mean-squaured (rms) over the odd-harmonic filtered waveforms."}
d_eeg %>% ggplot(aes(x = rms)) + 
    geom_histogram(binwidth = 0.2, fill = "skyblue", colour = "black") +
    theme_lucid()
```

### Threshold Data

@@

As above, a summary of the data.

@@

Again, we have a skewed distribution, so will fit with `family = 'lognormal'`.

### Control Data

@@

We can lok at the groups that only contain orientation, and see if we obtain the parametric response as documented in Kohler et al. (2016). We one might predict based on those results, we get a corresponding pattern of display duration thresholds, with the time taken to detect the symmetry dreasing as we increase the amount of rotational symmetry.

Curiosuly, we do not have a large difference betwee P4 and P6 in the eeg data.

```{r, fig.cap = "The effect of increasing the amount of rotational symmetry.", fig.height=3}
my_samples$eeg %>% select(P2, P3, P4, P6) %>%
  pivot_longer(names_to = "wallpaper group", cols = c(P2, P3, P4, P6)) %>% 
  mutate(exp = "eeg") %>%
  bind_rows(
    my_samples$threshold %>% select(P2, P3, P4, P6) %>% 
      pivot_longer(names_to = "wallpaper group", cols = c(P2, P3, P4, P6)) %>%
      mutate(exp = "display thresholds")) %>% 
  ggplot() + aes(x = value, fill = `wallpaper group`) + 
    geom_density(alpha = 0.35) + 
    facet_wrap(~ exp, scale = "free_y") + 
  theme_minimal() + 
  scale_fill_viridis_d()
```

>>>>

We now import the data. We have three variables: wallpaper group (wg), subject, and root-mean-squared amplitude (rms).

@@

If we plot the distribution of rms, we can clearly see that it is skewed. Furthermore, as negative rms amplitudes are impossible we will use a `lognormal` distribution to model these data.

```{r cache=TRUE, fig.cap = "Data are the root-mean-squaured (rms) amplitudes over the odd-harmonic filtered waveforms."}
d_eeg %>% ggplot(aes(x = rms)) + 
    geom_histogram(binwidth = 0.2, fill = "skyblue", colour = "black") +
    theme_lucid()
```

The table below shows how many groups per participant we have data for.

```{r}
d_eeg %>% group_by(subject) %>% summarise(count = n()) %>% knitr::kable()
```

## Threshold Data

@@

As above, a summary of the data. And again, we have a skewed distribution, (with negative display durations being impossible), so we will use also use a `lognormal` distribution to model the behaviour data.

@@

The table below shows how many groups per participant we have data for.

```{r}
d_dispthresh %>% group_by(subject) %>% summarise(count = n()) %>% knitr::kable()
```

## Control Data

@@

We can look at the groups that only contain orientation, and see if we obtain the parametric response as documented in Kohler et al. (2016). We will also investigate if we see the corresponding pattern with the display duration threshold data, with the time taken to detect the symmetry dreasing as we increase the amount of rotational symmetry.

```{r, cache = TRUE}
d_eeg %>% filter(wg %in% c("P2", "P3", "P4", "P6")) %>%
  mutate(orientation = parse_number(wg))-> d_eeg_rot

m_eeg_rot <- brm(data = d_eeg_rot, rms ~ orientation + (1|subject), family = "lognormal")

summary(m_eeg_rot)

d_eeg_rot %>% modelr::data_grid(orientation) %>%
  add_fitted_draws(m_eeg_rot, re_formula = NA, n=200) %>%
  ggplot() + 
  geom_line(data = d_eeg_rot, aes(x = orientation, y = rms, group = subject), alpha = 0.1, colour = "darkred") +
  geom_path(aes(x = orientation, y = .value, group = .draw), alpha = .1, colour = "royalblue2") + 
  theme_minimal() -> p1
```
```{r, cache = TRUE}
d_dispthresh %>% filter(wg %in% c("P2", "P3", "P4", "P6")) %>%
  mutate(orientation = parse_number(wg))-> d_disp_rot

m_disp_rot <- brm(data = d_disp_rot, threshold ~ orientation + (1|subject), family = "lognormal")

summary(m_disp_rot)

d_disp_rot %>% modelr::data_grid(orientation) %>%
  add_fitted_draws(m_disp_rot, re_formula = NA, n=200) %>%
  ggplot() + 
  geom_line(data = d_disp_rot, aes(x = orientation, y = threshold, group = subject), alpha = 0.1, colour = "darkred") +
  geom_path(aes(x = orientation, y = .value, group = .draw), alpha = .1, colour = "royalblue2") + 
  theme_minimal() -> p2
```

```{r}
p1 + p2
